EP1162_Prelim_Data_Screening

### 2020-03-02 data-raw/ep1162_prelimDataScreening.Rmd
final data checking

  # Trees with decreasing height measurements
 # write to .csv file
  x %>% 
   group_by(id) %>% 
   summarise(n=n()) %>% 
   filter(n>1) %>%  # filter tree records with more than one height measurement
   filter(id%in%names(which(mono.x==FALSE))) %>% 
   left_join(x,by="id") %>% 
   arrange(id) %>% 
   dplyr::select(Plot,TreeID,Species,Year,Height) %>% 
   pivot_wider(names_from="Year",values_from = "Height")

@@

>>>>

  # Trees with decreasing height measurements

  x %>% 
   group_by(id) %>% 
   summarise(n=n()) %>% 
   filter(n>1) %>%  # filter tree records with more than one height measurement
   filter(id%in%names(which(mono.x==FALSE))) %>% 
   left_join(x,by="id") %>% 
   arrange(id) %>% 
   dplyr::select(Plot,TreeID,Species,Year,Height) %>% 
   pivot_wider(names_from="Year",values_from = "Height")

@@

*** 
# FINAL SAVING
We'll save the final dataset and export it as well to .csv for final checks.

```{r}
dat %>% 
  write.csv(file=here::here("data-raw","ep1162_finalDataCheck.csv"))

dat %>% 
  save(file=here::here("data","ep1162_Data.RData")
